%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.75]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{3.1cm} % Uncomment to change the width of the dates column
\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name
\newcommand{\ulo}{\textsuperscript{\b{o}}}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Agust\'in} 
\familyname{Pivetta} 


\title{Curriculum Vitae}
\address{Jun\'in 683}{City of Buenos Aires}
\mobile{(+54 11) 5317-1037}
\email{aguspivetta@gmail.com}
\homepage{https://github.com/apivetta}{github.com/apivetta} 
\extrainfo{ar.linkedin.com/in/apivetta}
%\photo[70pt][0.4pt]{fotoCv.jpg}
%\quote{"Quote" - Author}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}


\cventry{Mar 2016 -- To date}{Full Stack Developer}{\textsc{Government of the city of Buenos Aires}}{Undersecretariat of Transit and Transport}{City of Buenos Aires}{
Duties:
\begin{itemize}
\item Design and implementation of IoT solutions on Microsoft Azure Cloud.
\item APIs and services development using Node.js and Python.
\item WebApp development using AngularJs.
\item Mobile apps development using Ionic Framework.
\item Dashboards and data visualizations using Leaflet and D3.js.
\end{itemize}}
\strut

%------------------------------------------------

\cventry{Dec 2015 -- Mar 2016}{Web UI Developer}{\textsc{Belatrix Software}}{City of Buenos Aires}{}{
Duties:
\begin{itemize}
\item Account: AOL.
\item WebApp development using AngularJs.
\item Testing with Jasmine and Protractor.
\end{itemize}}
\strut

%------------------------------------------------

\cventry{Sep 2014 -- Nov 2015}{Full Stack Developer}{\textsc{National Congress of Argentina}}{Parliamentary Digital Services}{City of Buenos Aires}{
Duties:
\begin{itemize}
\item WebApp development using AngularJs.
\item APIs and services development using Node.js and MongoDB.
\item APIs development using xQuery and eXistdb.
\end{itemize}}
\strut

%------------------------------------------------

\cventry{Feb 2013 -- Sep 2014}{SAP ABAP Developer}{\textsc{TGV Excelencia en Soluciones Inform\'aticas}}{City of Buenos Aires}{}{}
\strut

%------------------------------------------------

\cventry{Oct 2010 -- Oct 2012}{SAP ABAP Developer}{\textsc{Politec Argentina}}{City of Buenos Aires}{}{}
\strut


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{Ongoing}{Software Engineering}{CAECE University}{4th year}{Avg: 7}{Expected graduation date: Dec 2019}
\strut

%----------------------------------------------------------------------------------------
%	COURSES SECTION
%----------------------------------------------------------------------------------------

\section{Courses}

\cventry{Apr 2016}{Advanced Leaflet workshop}{\textsc{Conference for Free and Open Source Software for Geospatial}}{\textsc{National Geographic Institute}}{Duration: 8hs}{}
\strut
\cventry{Nov 2016}{Microsoft Azure training course}{}{\textsc{Microsoft}}{Duration: 40hs}{}{}
\strut
\cventry{Jan 2017}{Digital Transformation workshop}{Writing user stories applying Design Thinking techniques}{\textsc{Oracle}}{Duration: 8hs}{}{}
\strut

%\newpage


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Skills}
\subsection{Programming languages}
\cvitem{Proficient}{JavaScript/ES6, Node.Js, Python, xQuery, ABAP}
\cvitem{Working Knowledge}{Java, Scala, C/C++}
\strut

\subsection{Frameworks}
\cvitem{Front-end}{AngularJs, D3.js, Angular Material, Twitter Bootstrap, SASS, LESS }
\cvitem{Back-end}{Express.js, Socket.io}
\cvitem{Mobile}{Ionic}
\strut

\subsection{Tools}
\cvitem{}{JIRA, Visual Studio Team Services, Git, npm, Gulp, Webpack, Babel }
\strut

\subsection{Operating Systems and Platforms}
\cvitem{}{Linux, Windows, Microsoft Azure, Intel IoT Developer Kit, Arduino, Raspberry Pi}
\strut

\subsection{Databases}
\cvitem{}{MongoDB, Redis, PostgreSQL, PostGIS, MySQL/MariaDB, eXistDB }
\strut

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Language Skills}

\cvitemwithcomment{Spanish}{Native speaker}{}
\cvitemwithcomment{English}{Fluent}{}

\end{document}